\begin{acknowledgements}
Well, here we are. It's done. I have dreamed about doing a PhD in astrophysics for most of my life. Sure it's always different to how you first imagine it, in fact it has been the hard thing of my entire life but I have no regret for following my dream. However, success has been entirely dependent on quite a large number of people who I would like to include here. 

Firstly to Mrs Armitage - my narrowboat - for looking after me, keeping me going and teaching me to slow down and enjoy life whatever it throws at you. 

To my family, thank you for all your love and encouragement to keep going and find purpose in the monotonous times. 

To friends wherever you are, thanks. Thanks for pub trips, physics discussions, Burns Night poetry readings, frisbee, good times at good conferences, good times at bad conferences, and all things that friends are.

To my church lifegroup, you have kept my feet firmly on the ground when my head was spinning off in the heavens. Thank you for sharing all of real life with us. 

To my supervisor Martin, thank you for all that you've put up with and worked with. Thank you for the long hours of discussion and teaching that we had, your guidance over the project and your hard work in getting us to this point. 

Finally, to my wife Annie. This thesis belongs as much to you as it does to me. Without you this certainly wouldn't have happened. You believed in me when I didn't and made huge sacrifices for this DPhil, despite not having chosen it. I cannot thank you enough, and I'm not sure I will ever pay back the washing up debt I owe! I love you ``to the stars... and who says we have to come back?''
\end{acknowledgements}