\begin{originalitylong}
I, Joshua Warren, carried out the work in this thesis at the sub-department of Astrophysics, University of Oxford, between October 2014 and January 2018 under the supervision of Prof Martin Bureau. My research was funded by a Science and Technology Facilities Council (STFC) grant (Grant Code: 1577871). I declare that no part of this thesis has been submitted in support of another degree, diploma or other qualification at the University of Oxford or any other university. Except where otherwise stated the work in this thesis is all mine, in conjunction with the credited work by the rest of our research group consisting of Dr Isabella Prandoni and her PhD student Illaria Ruffa, Dr Robert Laing, Dr Paola Parma, Dr Hans de Ruiter, Dr Arturo Mignano, Prof Martin Bureau and I. All are based at the Italian National Institute for Astrophysics (INAF), except Dr Robert Laing who is based at Jodrell Bank and Prof Martin Bureau and I who are both at the University of Oxford.

We intend to shorten this thesis into a journal paper to be submitted to the Monthly Notices of the Royal Astronomical Society (\mnras) in early 2018, but currently no part of this thesis has been published. 

This thesis makes extensive use of observation from the Visible Multi-object Spectrograph \citep[VIMOS; ][]{LeFevre2003} and archival data from the Multi-unit Spectroscopic Explorer \citep[MUSE; ][]{Bacon2010}, both of which are mounted on the European Southern Observatory's (ESO's) Very Large Telescope (VLT). We also make use of observations from the Atacama Pathfinder Experiment \citep[APEX; ][]{Gusten2006} and the Atacama Large Millimeter/sub-millimeter Array (ALMA). ALMA is a partnership of ESO (representing its member states), the National Science Foundation (NSF; USA) and the National Institutes of Natural Sciences (NINS; Japan), together with the National Research Council (NRC; Canada), the Ministry of Science and Technology (MOST; Taiwan) and Academia Sinica Institute of Astronomy and Astrophysics (ASIAA; Taiwan), and Korea Astronomy and Space Science Institute (KASI; Republic of Korea), in cooperation with the Republic of Chile. The Joint ALMA Observatory is operated by ESO, Associated Universities Inc./National Radio Astronomy Observatory (AUI/NRAO; USA) and National Astronomical Observatory of Japan (NAOJ).

Within this thesis we make use of data products from the Two Micron All Sky Survey (2MASS), which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center (IPAC)/California Institute of Technology, funded by the National Aeronautics and Space Administration (NASA) and NSF. We also make use of the Set of Identifications, Measurements and Bibliography for astronomical Data (SIMBAD) database and Portal tool, operated at the Strasbourg astronomical Data Centre (CDS), France. In addition, observations made with the NASA/European Space Agency (ESA) \textit{Hubble Space Telescope}, and obtained from the Hubble Legacy Archive, which is a collaboration between the Space Telescope Science Institute (STScI/NASA), the Space Telescope European Coordinating Facility (ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC) are also used.

Finally, this research made use of the following resources and programs: arXiv.org; the Astrophysics Data System (ADS); \textsc{astropy}\footnote{\url{http://www.astropy.org}}, a community-developed core \textsc{python} package for astronomy \citep{TheAstropyCollaboration2013}; \textsc{kinemetry} \citep{Krajnovic2006}; \textsc{ipython} \citep{Perez2007}; \textsc{matplotlib} \citep{Hunter2007}; \textsc{p3d} \citep{Sandin2010, Sandin2011}; penalized pixel-fitting (\textsc{pPXF}; \citealt{Cappellari2004}); \textsc{py3d} \citep{Sanchez2011, Husemann2013, Husemann2014}; \textsc{scipy} \citep{Oliphant2007, Millman2011}; \textsc{numpy} \citep{VanderWalt2011}; \textsc{spectools} (Ryan Houghton and Simon Zieleniewski, private comm.); and \textsc{voronoi\_2d\_binning} \citep[including the SAURON colourmaps; ][]{Cappellari2003}.

The copyright of this thesis rests with the author. No quotation from it or information derived from it may be published without acknowledgement and, where appropriate, consent of its author.
\end{originalitylong}